Refinements for open automata

### 2022-01-27 2021-Refinement/paper/refinementarticle.tex
push rule factoorisation
work with rab

\begin{theorem}[Context refinement]
Let $A_1$, $A_2$ and $A_3$ be three open automata with $\wrel{A_1}{A_2}{H}$. 
Suppose that \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-locking.
We have: \[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\].
\end{theorem}

@@

We want to prove that $\mpar{R', H\cup J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$.
\begin{enumerate}
\item First, we have to prove:
\[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]

@@

\item We need to prove for any OT $t_{13}$ in $T_{13}$ originating from $s_{13}$:
\begin{align*}
		&  \OTx{13}{}{13}{13} \in \fOT{s_{13}}
\end{align*}		
there exists an indexed family $t_{23x}$ of OTs originating from $s_{23}$: 
\begin{align*}
		&  \mpar{\OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}
\end{align*}	
\begin{align*}		
		& \text{such that } \mpar{\forall x \in X, J'_{23x} \cap H' = J'_{13} \cap H'} \text{ and }\\
		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{align*}
where 
\begin{align*}
&V_{13}= V_1\uplus V^1_3 \text{ and }
V_{23}= V_2\uplus V^2_3\\
& H'=J_3'\uplus H \setminus \{k\} \subseteq J_3'\uplus \mpar{J_1' \cap J_2'} \setminus \{k\} = \mpar{J_3'\uplus J_1' \setminus \{k\} } \cap \mpar{J_3'\uplus J_2' \setminus \{k\}} = J_{13}'\cap J_{12}'\\
\end{align*}

@@

* either by the composition of a transition $t_1=\OTx{1}{}{1}{1}$ and a transition \[t_3^1=
\OT{ s^1_3}{{s^1_3}'}{\alpha_3^1}{ \uplus  {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{ g^1_3 }{ \psi^1_3} \qquad \text{ when } k \in J'_{1} 
\]. We obtain:
%%%% Attention deactiver ici
\[
\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, {s^1_3}'}}{\alpha_1}{\beta_{1j}^{j \in J'_1 \setminus \{k\}} \uplus  {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{g_1 \wedge g^1_3 \wedge \alpha^1_3 = \beta_{1k}}{\psi_1 \uplus \psi^1_3} \qquad \text{ where } k \in J'_{1} 
\]

* or by an the transition $t_1=\OTx{1}{}{1}{1}$ alone with the state $s^1_3$ unchanged, if $k \not\in J_1'$
\[\OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
\]
\medskip

By hypothesis we have $k \in H$, so in the case where $k \in J'_{1}$, we deduce that $k \in J'_{2x}$ we can  then build  a family of OTs $t_{23x}^{x\in X}$ with the same transitions of $A_3$ (up to renaming) as those used to build $t_{13}$. For any $t_{23x}$  there will then be two cases according on how it is built:

\[
\choice{
\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, {s^2_3}'}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{g_{2x} \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2xk}}{\psi_{2x} \uplus \psi^2_3} & \text{ if } k \in J'_{2x} \\
\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, s^2_3}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}}}{g_{2x}}{\psi_{2x}}& \text{otherwise}
}
\]

So have to prove the following:
\begin{align*}		
		&\mpar{\forall x \in X, J'_{23x} \cap H' = J'_{13} \cap H'} \text{ and }\\
		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{align*}

For all $x \in X$ we have to consider both  cases:
\begin{align*}
	\text{if } k \in J'_1:\quad &  J'_{23x} \cap H'  = 
	\mpar{ J'_{2x}\uplus J^{2 \prime}_{3}  \setminus \mbrc{k}} \cap  \mpar{J^{2 \prime}_{3} \uplus H \setminus \mbrc{k}} \\
		& = J^{2 \prime}_{3}  \uplus \mpar{J'_{2x} \cap H} \setminus \mbrc{k} \quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
		& = J^{1 \prime}_{3} \uplus \mpar{J'_1 \cap H} \setminus \mbrc{k} \\
		& = \mpar{ J'_1  \uplus J^{1 \prime}_{3}\setminus \mbrc{k}} \cap \mpar{J^{1 \prime}_{3} \uplus H \setminus \mbrc{k}}\\
		& = J'_{13} \cap H'\\
\text{if } k \notin J'_1:\quad &	J'_{23x} \cap H'  = \mpar{J'_{2x} \setminus \mbrc{k}} \cap \mpar{J^{2 \prime}_3 \uplus H \setminus \mbrc{k}} \\
\end{align*}

>>>>

\begin{theorem}[Context refinement]
Let $A_1$, $A_2$ and $A_3$ be three open automata with $\wrel{A_1}{A_2}{H}$. 
Let $J_3$ be the set of holes of $A_3$.
Suppose that \(k \in H\) and that \(A_1\subst{A_3}{k}\) is non-locking.
We have: \[\wrel{A_1\subst{A_3}{k}}{A_2\subst{A_3}{k}}{J_3 \uplus H \setminus \mbrc{k}}\].
\end{theorem}

@@

We want to prove that $\mpar{R', H\cup J_3 \setminus\{k\}}$ is a hole-tracking simulation of $A_{13}$ and $A_{23}$. In the following we denote $H'=H\cup J_3 \setminus\{k\}$
\begin{enumerate}
\item First, we have to prove:
\[\sigma_{013} \uplus \sigma_{023} \vdash R'\mpar{s_{013}, s_{023}}\]

@@

\item We need to prove for any OT $t_{13}$ in $T_{13}$ originating from $s_{13}$:
\begin{align*}
		&  \OTx{13}{}{13}{13} \in \fOT{s_{13}}
\end{align*}		
there exists an indexed family $t_{23x}$ of OTs originating from $s_{23}$: 
\begin{align*}
		&  \mpar{\OTx{23}{x}{23x}{23x} \in \fOT{s_{23}}}^{x \in X}
\end{align*}	
\begin{align*}		
		& \text{such that } \mpar{\forall x \in X, J'_{23x} \cap H' = J'_{13} \cap H'} \text{ and }\\
		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{align*}
Recall that 
\begin{align*}
&V_{13}= V_1\uplus V^1_3 \text{ and }
V_{23}= V_2\uplus V^2_3\\
& H' \subseteq J_3\uplus \mpar{J_1 \cap J_2} \setminus \{k\} = \mpar{J_3\uplus J_1 \setminus \{k\} } \cap \mpar{J_3\uplus J_2 \setminus \{k\}} \\
\end{align*}

@@

* either by the composition of a transition $t_1=\OTx{1}{}{1}{1}$ and a transition \[t_3^1=
\OT{ s^1_3}{{s^1_3}'}{\alpha_3^1}{   {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{ g^1_3 }{ \psi^1_3} \qquad \text{ when } k \in J'_{1} 
\]. We obtain:
%%%% Attention deactiver ici
\[
t_{13} = \OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, {s^1_3}'}}{\alpha_1}{\beta_{1j}^{j \in J'_1 \setminus \{k\}} \uplus  {(\beta^1_{3j})^{j \in J^{1 \prime}_3} }}{g_1 \wedge g^1_3 \wedge \alpha^1_3 = \beta_{1k}}{\psi_1 \uplus \psi^1_3} \qquad \text{ where } k \in J'_{1} 
\]

We then obtain a family of OTs by the simulation of $A_1$ by $A_2$ (stated above).
By hypothesis we have $k \in H$, so in the case where $k \in J'_{1}$, we deduce that $k \in J'_{2x}$ we can  then build  a family of OTs $t_{23x}^{x\in X}$ with the same transitions of $A_3$ (up to renaming) as those used to build $t_{13}$.
\[
t_{23x} = \left(\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, {s^2_3}'}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}  \setminus \{k\}} \uplus   {(\beta^2_{3j})^{j \in J^{2 \prime}_3} }}{g_{2x} \wedge g^2_3 \wedge \alpha^2_3 = \beta_{2xk}}{\psi_{2x} \uplus \psi^2_3}
\right)^{x\in X}\]
Recall that in this case  $k \in J'_{1}$

* or by an the transition $t_1=\OTx{1}{}{1}{1}$ alone with the state $s^1_3$ unchanged, if $k \not\in J_1'$
\[t_{13} = \OT{\mpar{s_1, s^1_3}}{\mpar{s'_1, s^1_3}}{\alpha_1}{\beta_{1j}^{j \in J'_1}}{g_1}{\psi_1}
\]
We then obtain a family of OTs by the simulation of $A_1$ by $A_2$ (stated above).
As  $k \in H$ we have $k \not\in J'_{2x}$ and we build:
\[t_{23x} = \left(
\OT{\mpar{s_2, s^2_3}}{\mpar{s'_{2x}, s^2_3}}{\alpha_{2x}}{\beta_{2xj}^{j \in J'_{2x}}}{g_{2x}}{\psi_{2x}} \right)^{x\in X}\]

These two cases define (depending on how $t_{13}$ is built) the family $t_{23x}$ of OTs we are looking for.
Thus, for both cases we have to prove the following:
\begin{align*}		
		&\mpar{\forall x \in X, J'_{23x} \cap H' =
 J'_{13} \cap H'} \text{ and }\\
		&  V_{13} \uplus V_{23} \uplus \fvars{t_{13}} \vdash R'\mpar{s_{13}, s_{23}} \wedge g_{13} \implies \operatorname*{\bigsymb{\bigvee}}_{x \in X} \mpar{\everymath{\displaystyle}\begin{array}{l}
			\alpha_{13} = \alpha_{23x} \wedge \bigwedge_\subbox{j \in J'_{23x} \cap H'} \beta_{13j} = \beta_{23xj} \\[12pt]
			\nwedge g_{23x} \wedge R'\mpar{s'_{13}, s'_{23x}}\psubst{\psi_{13} \uplus \psi_{23x}}
		\end{array}} 
	\end{align*}

For all $x \in X$ we have to consider both  cases:
\begin{align*}
	\text{if } k \in J'_1:\quad &  J'_{23x} \cap H'  
=((J'_{2x}  \setminus \mbrc{k})\uplus J^{2 \prime}_{3} ) \cap (H\uplus J_3 \setminus\{k\} )\\
&=((J'_{2x}\cap (H\uplus J_3))\uplus (J^{2 \prime}_{3}\cap (H\uplus J_3)))\setminus \mbrc{k}\\
&=((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}\cap  J_3))\setminus \mbrc{k}\text{ since } J_3\cap J'_{2x} = \emptyset \text{ and } H\cap J^{2 \prime}_{3} = \emptyset\\
& =((J'_{2x}\cap H)\uplus (J^{2 \prime}_{3}))\setminus \mbrc{k}\text{ since } J^{2 \prime}_{3}\subseteq J_3\\
& =(J'_1\cap H)\uplus (J^{1 \prime}_{3})\setminus \mbrc{k}\quad \text{ since } J^{1 \prime}_{3}=J^{2 \prime}_{3} \text{ and } J'_1 \cap H = J'_{2x} \cap H\\
& \text{faire reapparaitre J3 comme on l a elimine au dessus}\\
		& = \mpar{ J'_1  \uplus J^{1 \prime}_{3}\setminus \mbrc{k}} \cap \mpar{J_{3} \uplus H \setminus \mbrc{k}}\\
		& = J'_{13} \cap H'\\
\text{if } k \notin J'_1:\quad &	J'_{23x} \cap H'  = \mpar{J'_{2x} } \cap \mpar{J_3 \uplus H \setminus \mbrc{k}} \\
& = \mpar{J'_{2x}\cap H } \text{ since } J'_{2x}\cap J_3=\emptyset \land k\not\in J'_{2x} \\
& = \mpar{J'_1\cap H }\\
& = \mpar{J'_{13}\cap H' } \text{ since } J_3\cap J'_1=\emptyset \land k\not\in J_1'\\
\end{align*}
